\begin{acknowledgements}
\addchaptertocentry{\acknowledgementname} % Add the acknowledgements to the table of contents
It has been a long journey, and I am thankful to many people for their help in making this possible.

First of all, I thank my supervisory team, starting with Prof. Mark Billinghurst for his incredible inspiration and guidance throughout this work. I am so fortunate to have had the opportunity to learn from Mark throughout his time in Christchurch, Adelaide and Auckland, and many conferences overseas. I learned a lot about academic research, pushing the limits, and being kind to others. 
Special thanks to Dr Gun Lee for his generous motivation and kindness since the beginning despite his busy schedule and move to Adelaide. I'm grateful for Gun for sharing his knowledge in experiment design and statistics, and for being patient and supportive when answering my questions. 
I also thank Assoc. Prof. Tobias Langlotz for his critical and constructive feedback, and for taking the time to Skype regularly and meet at conferences overseas.
Many thanks to Prof. Robert W. Lindeman for his support and review of this work, providing access to devices, supporting students to go to conferences. I appreciate the paper-review meetings, and his encouragement to learn and collaborate with other students in the lab. 

Thanks to Prof. Anthony Steed for his review during his visit to HIT Lab NZ, and to Prof. Tobias Höllerer and Prof. Steven Feiner for their valuable feedback during the doctoral consortium at ISMAR 2018. I would also like to thank the examiners of this thesis for taking the time to read and evaluate this work. 

I would not have been able to complete this thesis without the support of the staff and students at the HIT Lab NZ. Thanks to Ken, Greg, Mel, Chris, Huidong, Thammathip, David, Hyungon, Bhuvaneswari, Rory, Humayun, Nikita, Yuanjie, Kiên, Kris, Merel, Hendrik and Lucie for all the great time and memories during my study. Thanks for the kind people at Jade Software for giving me flexible working hours so I can work on my thesis.

I'm thankful to my family back in Syria, to my parents and to my four siblings for their support despite the distance.
% I lost my wife during this journey, I didn't pay enough attention to what she needed, but 
I'm in debt to Boushra for her love, patience and for standing beside me for most of this journey. 

Thank you all very much!!
\end{acknowledgements}