\chapter{Interaction Continuum} % Main chapter title
\label{ch:annotation} % Change X to a consecutive number; for referencing this chapter elsewhere, use \ref{ChapterX}

After studying the representation of social contacts (Chapter~\ref{ch:contacts}) and shared social data (Chapter~\ref{ch:data}), this chapter studies the interactions between social contacts with each other and other virtual objects. The interaction is represented by adding an AR tag or annotation on a shared medium to socially connect with other users. 
The aim of this chapter is to answer the research question \ref{rq:data}: "How wearable AR displays can be used best for interacting with social contacts and shared social data?"
Annotation is one of the social interaction methods where users can add text or other information to be overlaid on top of a shared medium for the purpose of communicating ideas or thoughts between participants. In this chapter, we explore different media and options for sharing annotations with social contacts. AR annotations are useful for remote collaboration and shared experiences where context or descriptions of the conversation can be highlighted.  
The first section \ref{sec:video} addresses annotation of a live video stream. The second section \ref{sec:3D} studies annotation of a 3D environment using 3D sensors to detect the shared surrounding environment. The last section \ref{sec:pano} looks into panorama images as a medium and explores awareness and collaboration techniques. 

\input{Chapters/61-video}
\input{Chapters/62-3d}
\input{Chapters/63-pano}
\input{Chapters/69-summary}
